---
title: "MSGARCH Analysis"
author: "Euclid Zhang"
date: "11/01/2022"
output:
  pdf_document: default
  html_document: default
---


MSGARCH Analysis
CUNY SPS MSDS
Professor Samuel Gralnick
Team Sugar Cane: Euclid Zhang, Jie Zou, Zhenni Xie
Fall 2022



Previously, we demonstrated how to construct a GARCH model to analyze the volatility of an asset with heteroscedastic returns. In this analysis, we will examine if the Markov-Switching GARCH model performs better than the plain vanilla GARCH model in modeling the changing volatility of an investment asset. 

We use the MSGARCH package in R to construct our model. The package provides two methods of constructing an MSGARCH model, the Maximum Likelihood method and the MCMC/ Bayesian method. We will focus on the MCMC/ Bayesian method in this analysis.


```{r message = FALSE}
#loading libraries

library('yfR')
library('stringr')
library('dplyr')
library('tidyr')
```


Our investment portfolio includes the following assets. In this analysis, we will focus on the equity assets.


```{r}
#load the asset information of our portfolio
stocks <- read.csv("portfolio assets.csv", stringsAsFactors = FALSE, na = c(""))
stocks
```

Download the daily trading prices from Yahoo, using the yfR package

```{r message=FALSE}
#download the asset prices
stock_prices <- yf_get(
  tickers = stocks$Ticker[-1],
  first_date = as.Date('2021-10-29'),
  last_date = as.Date('2022-10-29'),
  thresh_bad_data  = 1,
  freq_data = "daily"
)
stock_prices
```


We will use the adjusted price in this analysis. The data is reshaped so that the price of each asset is in one column 

```{r}
#using the adjusted close price only for our analysis
stock_prices2 <- stock_prices[c('ticker','ref_date','price_adjusted')]
#convert the data from long to wide
stock_prices2 <- spread(stock_prices2, key = ticker, value = price_adjusted, fill = NA)
#remove date for easier data frame manipulations
stock_prices2$ref_date = NULL
stock_prices2
```

We then calculate the daily log return of the assets

```{r}
#calculate the log return
log_return <- log(stock_prices2[-1,]/stock_prices2[1:(nrow(stock_prices2)-1),])
```


We will demonstrate the MSGARCH process using one of our assets, 'HSON', as an example. 

```{r}
#create the time series 
return_ts = ts(log_return['HSON'])
```

```{r}
library("MSGARCH")

set.seed(618)

#seed = 32
#13 25 26-4
#set.seed(seed)
```

The following is the summary of the MSGARCH model with the number of states K=2. 

```{r}

msgarch.k2 <- CreateSpec(variance.spec = list(model = "sGARCH"),
                          distribution.spec = list(distribution = "norm"),
                          switch.spec = list(K = 2))
fit.mcmc.k2 <- FitMCMC(spec = msgarch.k2, data = return_ts)
summary(fit.mcmc.k2)
```

The following are the predicted volatility for the next 10 days.

```{r}
pred <- predict(fit.mcmc.k2, nahead = 10, do.return.draw = TRUE)
pred$vol
```

The MSGARCH package also has built-in functions to calculate the VaR and Expected Shortfall of the predictions. These are useful tools for our investment risk management.

```{r}
risk <- Risk(fit.mcmc.k2, alpha = c(0.01, 0.05), nahead = 10)
risk$VaR
risk$ES
```


We can compare the estimated volatilities of the MSGARCH (K=2) and the simple GARCH, which is a MSGARCH model with a number of states K=1. 



```{r}
set.seed(seed)

msgarch.k2 <- CreateSpec(variance.spec = list(model = "sGARCH"),
                          distribution.spec = list(distribution = "norm"),
                          switch.spec = list(K = 2))
fit.mcmc.k2 <- FitMCMC(spec = msgarch.k2, data = return_ts)

```



```{r}
plot(return_ts, type = 'l', las = 1, lwd = 1, xlab = "Date",
     ylab = "Return", col = "black", cex.axis = 1.5, cex.lab = 1.5, pch = 19)
lines(1.96*Volatility(fit.mcmc.k1), type = 'l', col = "red")
lines(-1.96*Volatility(fit.mcmc.k1), type = 'l', col = "red")
lines(1.96*Volatility(fit.mcmc.k2), type = 'l', col = "blue")
lines(-1.96*Volatility(fit.mcmc.k2), type = 'l', col = "blue")
legend(x="topleft", legend=c("K=1", "K=2"),
       col=c("red", "blue"), lty=1, cex=0.8)
```


```{r}
# plot(return_ts, type = 'l', las = 1, lwd = 1, xlab = "Date",
#      ylab = "Return", col = "black", cex.axis = 1.5, cex.lab = 1.5, pch = 19)
# lines(1.96*Volatility(fit.mcmc.k1), type = 'l', col = "red")
# lines(-1.96*Volatility(fit.mcmc.k1), type = 'l', col = "red")
# lines(1.96*Volatility(fit.mcmc.k2), type = 'l', col = "blue")
# lines(-1.96*Volatility(fit.mcmc.k2), type = 'l', col = "blue")
# lines(1.96*Volatility(fit.mcmc.k4), type = 'l', col = "orange")
# lines(-1.96*Volatility(fit.mcmc.k4), type = 'l', col = "orange")
# lines(1.96*Volatility(fit.mcmc.k5), type = 'l', col = "purple")
# lines(-1.96*Volatility(fit.mcmc.k5), type = 'l', col = "purple")
# legend(x="topleft", legend=c("K=1", "K=2","K=3","K=5"),
#        col=c("red", "blue", "orange","purple"), lty=1, cex=0.8)
```



```{r}
# plot(return_ts, type = 'l', las = 1, lwd = 1, xlab = "Date", ylim = c(-2.2,2.2),
#      ylab = "Return", col = "black", cex.axis = 1.5, cex.lab = 1.5, pch = 19)
# lines(1.96*Volatility(fit.mcmc.k1), type = 'l', col = "red")
# lines(-1.96*Volatility(fit.mcmc.k1), type = 'l', col = "red")
# lines(1.96*Volatility(fit.mcmc.k2), type = 'l', col = "blue")
# lines(-1.96*Volatility(fit.mcmc.k2), type = 'l', col = "blue")
# lines(1.96*Volatility(fit.mcmc.k3), type = 'l', col = "green")
# lines(-1.96*Volatility(fit.mcmc.k3), type = 'l', col = "green")
# lines(1.96*Volatility(fit.mcmc.k4), type = 'l', col = "orange")
# lines(-1.96*Volatility(fit.mcmc.k4), type = 'l', col = "orange")
# lines(1.96*Volatility(fit.mcmc.k5), type = 'l', col = "purple")
# lines(-1.96*Volatility(fit.mcmc.k5), type = 'l', col = "purple")
# legend(x="topleft", legend=c("K=1", "K=2","K=3","K=4","K=5"),
#        col=c("red", "blue", "green", "orange","purple"), lty=1, cex=0.8)
```


